---
title: "Homework 2"
output: github_document
Name: Jasmin Martinez
Date: 10/02/24
---
### **Problem 1**

Loading in data and clean variable names: 
```{r}
library(readr)
library(dplyr)

nyc_subway = read.csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")
```

Retain specified variables 
```{r}
nyc_subway = select(nyc_subway, Line, Station.Name, Station.Latitude, Station.Longitude, Route1:Route11, Entrance.Type, Entry, Vending, ADA)
```

Modify ENTRY variable 
```{r}
nyc_subway$Entry.Logical = ifelse(nyc_subway$Entry == "YES", TRUE, FALSE)
```

**About this data set:** 

This data set is called "nyc_subway" and contains the following variables: line, station name, station latitude, station longitude, route (1-11), entrance type, entry, vending, and ADA compliance. 

I began by loading in the data and viewing it, I did not provide that in the output document given the data set is large. Then, I retained the variables listed above in the data set using the 'select' function. Finally, I created a new variable, Entry.logical. This new variable takes the Entry variable values and modifies the new variable to be True/False. I chose to make a new variable in this case to ensure the function was being run/used correctly without making permanent changes to the Entry variable. 

The data set has 20 variables and 1,868 observations. This data set would be considered tidy because the columns are variables and the rows are observations and every value has a cell. 

**Data set questions:** 

There are **465** distinct stations in this data set, this consists of stations with different lines and station names. 
```{r echo=TRUE}
distinct_station = distinct(nyc_subway, Line, Station.Name)
count(distinct_station)
```

There are **468** stations that are ADA compliant. 
```{r echo=TRUE}
ADA_compliant = filter(nyc_subway, ADA == TRUE)
count(ADA_compliant)

```

There are **69** station entrances/exits without vending that allow entrance. 
```{r echo=TRUE}
novending_yesentry = filter(nyc_subway, Vending == "NO", Entry == "YES")
count(novending_yesentry)
```

**Reformatting data:**

### **Problem 2**
Importing data from excel file
```{r echo=TRUE}
library(readxl)
library(tidyr)

trash_wheel = read_excel("./data/202409 Trash Wheel Collection Data.xlsx", sheet = "Mr. Trash Wheel")
```

Cleaning data
```{r}
trash_wheel = 
  janitor::clean_names(trash_wheel) %>%
  select(dumpster, month, year, date, weight_tons, volume_cubic_yards, plastic_bottles, polystyrene, cigarette_butts, glass_bottles, plastic_bags, wrappers, sports_balls, homes_powered) %>%
  rename(weight = weight_tons, volume = volume_cubic_yards) %>% 
  drop_na(dumpster)


trash_wheel$sports_balls = round(trash_wheel$sports_balls)
trash_wheel$sports_balls = as.integer(trash_wheel$sports_balls)
trash_wheel$year = as.numeric(trash_wheel$year)

trash_wheel$wheel_id = "TW"
```

_Professor Trash Wheel Data_

Importing data from excel file
```{r}
prof_trash_wheel = read_excel("./data/202409 Trash Wheel Collection Data.xlsx", sheet = "Professor Trash Wheel")
```

Cleaning Data
```{r}
prof_trash_wheel = 
  janitor::clean_names(prof_trash_wheel) %>%
  rename(weight = weight_tons, volume = volume_cubic_yards) %>% 
  drop_na(dumpster)
  

prof_trash_wheel$wheel_id = "PTW"
```

_Gwynnda Data_

Import data
```{r}
gwynnda_trash_wheel = read_excel("./data/202409 Trash Wheel Collection Data.xlsx", sheet = "Gwynnda Trash Wheel")
```

Cleaning Data
```{r}
gwynnda_trash_wheel = 
  janitor::clean_names(gwynnda_trash_wheel) %>%
  rename(weight = weight_tons, volume = volume_cubic_yards) %>% 
  drop_na(dumpster)

gwynnda_trash_wheel$wheel_id = "GTW"
```

Combine the data sets 
```{r}
merged_trash_wheel = bind_rows(trash_wheel, prof_trash_wheel, gwynnda_trash_wheel)
head(merged_trash_wheel)
```

Answering questions
```{r}
dump_total = merged_trash_wheel %>% 
  filter(wheel_id == "PTW")
dump_total = sum(dump_total$weight,na.rm=TRUE)
dump_total

cigs_total = merged_trash_wheel %>% 
  filter(wheel_id == "GTW", year ==2022, month == "June")

cigs_total = sum(cigs_total$cigarette_butts, na.rm=TRUE)
cigs_total

```
The data set has 1033 observations and one key variables include dumpster number, year, and wheel_id. The total weight of trash collected by Professor Trash Wheel is 246.74 tons. The total number of cigarette butts collected by Gwynnda in June 2022 was 18120. 


### **Problem 3**

Import data 
```{r}
baker_df = read.csv("./data/gbb_datasets/bakers.csv") %>% 
    rename(baker = Baker.Name)
bakes_df = read.csv("./data/gbb_datasets/bakes.csv") %>% 
  rename(series = Series, episode = Episode, baker = Baker)

results_df = read.csv("./data/gbb_datasets/results.csv", header = TRUE, skip = 2)
```

I imported the three data frames to be merged. First, I adjusted the variable name "baker" to be consist across all the data frames, since this will be the variable I will use to merge the three data frames. 
















