---
title: "Homework 2"
output: github_document
Name: Jasmin Martinez
Date: 10/02/24
---
### **Problem 1**

Loading in data and clean variable names: 
```{r}
library(readr)
library(dplyr)

nyc_subway = read.csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")
```

Retain specified variables 
```{r}
nyc_subway = select(nyc_subway, Line, Station.Name, Station.Latitude, Station.Longitude, Route1:Route11, Entrance.Type, Entry, Vending, ADA)
```

Modify ENTRY variable 
```{r}
nyc_subway$Entry.Logical = ifelse(nyc_subway$Entry == "YES", TRUE, FALSE)
```

**About this data set:** 

This data set is called "nyc_subway" and contains the following variables: line, station name, station latitude, station longitude, route (1-11), entrance type, entry, vending, and ADA compliance. 

I began by loading in the data and viewing it, I did not provide that in the output document given the data set is large. Then, I retained the variables listed above in the data set using the 'select' function. Finally, I created a new variable, Entry.logical. This new variable takes the Entry variable values and modifies the new variable to be True/False. I chose to make a new variable in this case to ensure the function was being run/used correctly without making permanent changes to the Entry variable. 

### **Problem 2**

### **Problem 3**
